25 years of Social Work Research

### 2015-02-21 dataCleaning.Rmd
Added code to toggle between directories for our computers

load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoPsycInfo.R")
```

@@

# Set the working directory
#setwd("/Users/beperron/Git/SocialWorkResearch/Data")
```

>>>>

load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoPsycInfo.R")

#load("/Users/SSW/GitHub/SocialWork100Years/Data/ebscoFULL.R")
#load("/Users/SSW/GitHub/SocialWork100Years/Data/proQuest.R")
#load("/Users/SSW/GitHub/SocialWork100Years/Data/ebscoPsycInfo.R")

```

@@

# Set the working directory
#setwd("/Users/beperron/Git/SocialWorkResearch/Data")
#setwd("/Users/SSW/GitHub/SocialWork100Years/Data")
```
